Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles: Supplementary information

### 2021-08-05 source/jeb_tex/supplementary.tex
responded to Reviewer 2 comments.
updated MS and figures and supplementary based on his elaborate comments.

\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information}

@@

Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
bridge'') was calculated by performing simulations in Surface Evolver
\cite{RN206}, similar to the method described by \citet{RN93}.
A simple cubic geometry, mimicking the capillary bridge, of constant
volume, $V$, was defined as the initial condition with an interfacial
tension, $\gamma$, with the surrounding medium. Interfacial tension
of the capillary bridge with the substrate is given by $\gamma\cos\theta$,
where $\theta$ is the corresponding contact angle inside the bridge.
For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
surrounding water, since $\theta$ can also directly characterise
the substrate wettability. The capillary bridge spans a gap distance
$d$ between the top face and the substrate. The boundary conditions
were set corresponding to a pinned contact line of diameter $D$ on
the top face and constant interfacial tension with the substrate on
the bottom. All lengths were normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
An appropriate geometry refinement routine was chosen to evolve the
capillary bridge shape to its minimum energy state. The normalised
total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
pressure and surface tension contributions , where:

@@

The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) was characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
\end{table}

@@

Capillary force of a single air bubble against a PFOTS-coated glass surface are compared
for two different volumes (Figure \ref{fig:Bubble_capillary_force}). The volumes correspond to the expected
range for the case of the trapped air bubble in a ladybug's pad. Here, the bubble
was pinned to a micropatterned PDMS substrate on the top. Approach-retract tests were performed
at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
adhesion force of any of the bubbles never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible. Example measurement video is included in the supplementary data (Movie3).

>>>>

\title{Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles: Supplementary information}

@@

Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
bridge'') was calculated by performing simulations in Surface Evolver
\cite{RN206}, similar to the method described by \citet{RN93}.
A simple cubic geometry, mimicking the capillary bridge, of constant
volume, $V$, was defined as the initial condition with an interfacial
tension, $\gamma$, with the surrounding medium. Interfacial tension
of the capillary bridge with the substrate is given by $\gamma\cos\theta$,
where $\theta$ is the corresponding contact angle inside the bridge.
For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
surrounding water, since $\theta$ can also directly characterise
the substrate wettability. The capillary bridge spans a gap distance
$d$ between the top face and the substrate. The boundary conditions
were set corresponding to a pinned contact line of diameter $D$ on
the top face and constant interfacial tension with the substrate on
the bottom. All lengths were normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
An appropriate refinement and iteration routine was chosen by trial-and-error to get a stable converged solution corresponding to the minimum energy state of the capillary bridge surface. The normalised
total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
pressure and surface tension contributions , where:

@@

The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) was characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}). De-gassed water showed similar contact angle values as normal water.
\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
\end{table}

@@

Capillary force of a single air bubble against a PFOTS-coated glass surface are compared
for two different volumes (Figure \ref{fig:Bubble_capillary_force}). The volumes correspond to the expected
range for the case of the trapped air bubble in a ladybug's pad. Here, the bubble
was pinned to a micropatterned PDMS substrate on the top. Approach-retract tests were performed
at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
adhesion force of any of the bubbles never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible (< 10 \%). Example measurement video is included in the supplementary data (Movie3).
